### 2025-02-27 paper/relatedwork.tex
Comment on indexed streams.

Another related approach is the Etch compiler for indexed
streams~\cite{10.1145/3591268}, which is implemented as an embedded
language in Lean. Although the domain differs from ours, stream/tensor
contraction as compared to array programming, the basic idea of
extracting low level code is similar. Significant differences include
our support for rank polymorphism, automatic differentiation, and
parallel execution.

>>>>

Another related approach is the Etch compiler for indexed
streams~\cite{10.1145/3591268}, which is implemented as an embedded
language in Lean.  This work is very similar in spirit and it gives
a general encoding for sparse array computations.  The key difference
is that indexed streams fix traversal order of the index-space
of the given array, whereas \AD{Ar} only describes a mapping.
In fact indexed streams could be used to implement \AF{Ar}
computations.  It is a little unclear how to handle parallelism
in indexed streams.  \AF{Ar} expressions can always run parallel,
and this is one of the reasons why we can map them so easily to GPUs.
